What can GitHub and Googlecode Issues tell us about Exceptions in Android?

### 2014-08-25 android-stacks.tex
restructuring section 3

\textbf{I-Checked exceptions should be used to represent recoverable
conditions} (\cite{mandrioli1992advances,gosling2000java,wirfs2006toward,bloch2008effective})
The developer should use checked exceptions for conditions from which the caller
is expected to recover. By confronting the API user with a checked exception,
the API designer is forcing the client to handle the exceptional condition. The
client can explicitly ignore the exception (swallowing, or converting it to
other type) at the expense of the program's robustness~\cite{gosling2000java}.

\textbf{II-Error represents an unrecoverable condition detected by the JVM which
should not he handled} (\cite{gosling2000java}). It results from failures detected
by the Java Virtual Machine which indicate resource deficiencies, invariant
failures or other conditions that make impossible the program to recover.

@@

\textbf{III-A method should throw exceptions that precisely define the
exceptional condition} (\cite{gosling2000java,bloch2008effective}). To do so,
developers should either try to reuse the exception types already defined in the
JVM or they should create a specific exception. Throwing general types such as a
pure java.lang.Exception or a java.lang.RuntimeException is considered a bad practice.

@@

\textbf{IV- All exceptions explicitly thrown by a method should be documented.}
(\cite{mandrioli1992advances,gosling2000java,wirfs2006toward,bloch2008effective}).
The exceptions thrown by a method are an important part of methods interface,
and is required to use the method properly. The checked exceptions are already
part of the  methods signature, and the method caller is aware of the checked
exceptions being thrown by it. According to~\cite{bloch2008effective}, it is
also wise to document the explicitly thrown runtime exceptions\footnote{This
excludes the implicitly signaled JVM runtime exceptions related to programming
mistakes} as carefully as checked exceptions. Doing so, the clients of a method
will be aware of all the exceptions the method can throw. If the developer fails to
do follow this practice (specially when developing library code) it will be
difficult or even impossible for the caller to make effective use of such 
method~\cite{wirfs2006toward, bloch2008effective} and protect its code
against unforeseen exceptions.

@@

\section{Study Design}

This work describes an exploratory study which was based on a sequential
mixed-methods approach~\cite{ivankova2006using} for collecting, analyzing, and
integrating both quantitative and qualitative evidence along the stages of the
research process.

Based mainly on the information available on exception stack traces embedded 
on Github issues, the goal of this study was to gain a better understanding 
of exception-related system crashes.

 More specifically, we aimed at answering
the following research questions:

@@

  \item[RQ1] What are the common characteristics of exception stack traces reported on issues?/What are the main causes of crashes reported on issues? (more explicit?)

@@

@@

\subsection{Github Data}
\label{sec:git}

@@

\subsubsection{GHTorrent Dataset} This study used the dataset provided by the GHTorrent project~\cite{Gousi13}, an off-line mirror of the data 
offered through the Github API.  GHTorrent has been collecting data from Git since 
February 2012. Up to Dec 2013, and when we queried GHTorrent, it included 332,864 non-fork Java
repositories \footnote {A Java project is specified in GitHub with a
specific label.}  from which only 44,323 have contained at least issue report in their lifetime. From this set only 16,837 were watched by external users. To ensure that our work targets projects that are openly used by
users other than their developers, we focused our analysis on just those projects.

@@

\subsubsection{Google Code}

@@

\subsubsection{Exception Stack Traces on Issues}

@@

\subsubsection{Distiling Exception Stack Trace Information}

\- root exception

\- signaler
\- method
\- class
\- package

\- Exception

\subsubsection{Android Apps Selection}
\label{sec:android}

 % SELECT id, exception, exception_extends, exception_from, exception_package, 
 %      issueid_onexminer, main_cause, main_extends, main_from, main_package, 
 %      main_pre_signaler_java, main_signaler, mainsignaler_class, mainsignaler_from, 
 %      mainsignaler_method, mainsignaler_package, pre_signaler_java, 
 %      repo, root_cause, root_extends, root_from, root_package, root_pre_signaler_java, 
 %      root_signaler, rootsignaler_class, rootsignaler_from, rootsignaler_method, 
 %      rootsignaler_package, signaler, signaler_class, signaler_from, 
 %      signaler_method, signaler_package, stack
 % FROM stacktracesummary;

\subsection{The Mining Process}
\label{sec:miningproc}

@@

\begin{figure*}
\centering
\includegraphics[width=\hsize]{overview.pdf}
\caption{Overview of the study based on mixed approaches.}
\label{fig:overviewfig}
\end{figure*}

@@

OBS: THE PICTURE WILL BE UPDATED TO REFLECT THIS PROCESS DESCRIPTION.

\noindent\emph{StackTraceMiner and Distiller} The first step in the process is
mining references to exceptions and stack traces embedded in issues, distilling
the information that composes a stack trace and storing the results in a
relational database. Some of the information extracted from the stack traces were:
 the exception being thrown, its signaler, the exception root cause, its corresponding signaler,
and packages related to each one of these fields.
The tool is based on a combination between a regular expression based parser 
with heuristics able to identify and filter exception names and stack traces inline with text. In
contrast to existing issue parsing solutions such as Infozilla, the parser
created in this work can extract all causes related to an exception on a stack,
and stack traces embedded in logs files.

%\section{Study Operation and Results}
Next section presents the results for each of the study phases, providing both a
quantitative and qualitative analysis of the outcomes.

@@

\subsection{Characterizing the Most Common Exceptions}

>>>>

%\textbf{I
\emph{I-Checked exceptions should be used to represent recoverable
conditions} (\cite{mandrioli1992advances,gosling2000java,wirfs2006toward,bloch2008effective})
The developer should use checked exceptions for conditions from which the caller
is expected to recover. By confronting the API user with a checked exception,
the API designer is forcing the client to handle the exceptional condition. The
client can explicitly ignore the exception (swallowing, or converting it to
other type) at the expense of the program's robustness~\cite{gosling2000java}.

\emph{II-Error represents an unrecoverable condition detected by the JVM which
should not he handled} (\cite{gosling2000java}). It results from failures detected
by the Java Virtual Machine which indicate resource deficiencies, invariant
failures or other conditions that make impossible the program to recover.

@@

\emph{III-A method should throw exceptions that precisely define the
exceptional condition} (\cite{gosling2000java,bloch2008effective}). To do so,
developers should either try to reuse the exception types already defined in the
JVM or they should create a specific exception. Throwing general types such as a
pure java.lang.Exception or a java.lang.RuntimeException is considered a bad practice.

@@

\emph{IV- All exceptions explicitly thrown by a method should be documented.}
(\cite{mandrioli1992advances,gosling2000java,wirfs2006toward,bloch2008effective}).
The exceptions thrown by a method are an important part of methods interface,
and is required to use the method properly. The checked exceptions are already
part of the  methods signature, and the method caller is aware of the checked
exceptions being thrown by it. According to~\cite{bloch2008effective}, it is
also wise to document the explicitly thrown runtime exceptions\footnote{This
excludes the implicitly signaled JVM runtime exceptions related to programming
mistakes} as carefully as checked exceptions. Doing so, the clients of a method
will be aware of all the exceptions the method can throw. If the developer fails to
do follow this practice (specially when developing library code) it will be
difficult or even impossible for the caller to make effective use of such 
method~\cite{wirfs2006toward, bloch2008effective} and protect its code
against unforeseen exceptions.

@@

\section{Empirical Study Design}

The goal of this study was to extract nformation available on exception stack 
traces embedded on issues reported on Android projects, looking for the common characteristics of
those issues and investigating whether they could reveal common defficiencies
on the exception handling code of both the applications and the underlaying 
 framework.

We choose Android apps because it is the only top platform that is open-source,
and due to its increasing popularity it xxxx.

Our study focused on free apps, since the information needed to perform our study
cannot be retrieved from commercial apps because their issue reports and their
source code is not publicly available. The Android open-source apps were also 
target of other research studies [fse2013][ahimed].

\subsection{Research Questions}
In the context of our study we formulated the following reseach questions:

@@

  \item[RQ1] \noindent\emph{What are the common characteristics of exception stack traces reported on issues?} What are the main causes of crashes reported on issues? (more explicit?)

@@

%Based mainly on the information available on exception stack traces embedded 
%on issues, the goal of this study was to gain a better understanding 
%of exception-related system crashes.

@@

\subsection{Data Extraction Process}
\label{sec:miningproc}

The data used in our study to answer our research questions are: the issues related to each 
Android project available in each repository; the source code and manifest file of each application;
the bytecode of all exceptions defined and reused by Android platform.

\subsubsection{Android Apps in GitHub}
\label{sec:git}

@@

RESUMIR:
This study used the dataset provided by the GHTorrent project~\cite{Gousi13}, an off-line mirror of the data 
offered through the Github API.  GHTorrent has been collecting data from Git since 
February 2012. Up to Dec 2013, and when we queried GHTorrent, it included 332,864 non-fork Java
repositories \footnote {A Java project is specified in GitHub with a
specific label.}  from which only 44,323 have contained at least issue report in their lifetime. From this set only 16,837 were watched by external users. To ensure that our work targets projects that are openly used by
users other than their developers, we focused our analysis on just those projects.

@@

\subsubsection{Android Apps in GoogleCode}

@@

\noindent\emph{Exception StackTrace Miner} The first step in the process is
mining references to exceptions and stack traces embedded in issues, d
GitHub Commector, and GoogleCode Issue Crawler.

\noindent\emph{Exception Stack Trace Distiller} 
Distills the information that composes a stack trace and storing the results in a
relational database. Some of the information extracted from the stack traces were:
 the exception being thrown, its signaler, the exception root cause, its corresponding signaler,
and packages related to each one of these fields.
The tool is based on a combination between a regular expression based parser 
with heuristics able to identify and filter exception names and stack traces inline with text. In
contrast to existing issue parsing solutions such as Infozilla, the parser
created in this work can extract all causes related to an exception on a stack,
and stack traces embedded in logs files.
AS PRESENTED IN FIGURE X

\subsubsection{The ExceptionMiner Tool}

@@

\subsubsection{Data Filtering and Manual Inspections}

COMPLETE HERE.....

\subsubsection{Database of Exception Stack Trace Information}
\subsubsection{Distiling Exception Stack Trace Information}

\- root exception
\- signaler
\- method
\- class
\- package
\- Exception

\subsection{Process}

ESPALHAR ESTA SECAO NAS OUTRAS.

@@

%\begin{figure*}
%\centering
%\includegraphics[width=\hsize]{overview.pdf}
%\caption{Overview of the study based on mixed approaches.}
%\label{fig:overviewfig}
%\end{figure*}

@@

\subsection{Replication Package}
All the data used in this study will be publicly available at http://.....
Specifically we provide: (i) all issues related to Android projects found
in GITHub and GoogleCode used in this study; (iii) all stack traces extracted
from issues (ii) the results of manual inspection steps; (iv) the tool developed 
in this work to support stack trace extraction and distilling.

Next section presents the results for each of the study phases, providing both a
quantitative and qualitative analysis of the outcomes.

@@

\subsection{Characterizing the Most Common Root Exceptions}
